Untitled

### 2021-01-27 ms/manuscript.Rmd
Move pretty_text() to functions.R

# Define color-blind palette
cbPalette <- c(grey = "#999999", gold = "#E69F00", skyblue = "#56B4E9", 
               green = "#009E73", yellow = "#F0E442", blue = "#0072B2", 
               red = "#D55E00", purple = "#CC79A7")

# Define function for formatting text in legends
pretty_text <- function (x) {
  x %>%
  str_replace_all("_", " ") %>%
    str_to_sentence()
}
```

>>>>

# Define color-blind palette
cbPalette <- c(grey = "#999999", gold = "#E69F00", skyblue = "#56B4E9", 
               green = "#009E73", yellow = "#F0E442", blue = "#0072B2", 
               red = "#D55E00", purple = "#CC79A7")
```
